How do we get from object recognition\\ to object naming?

### 2018-07-02 papers/SiVL2018/objectnaming.tex
Adds first draft of structure; splits sections into files

% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{booktabs}
\usepackage{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV18SubNumber{***}  % Insert your submission number here

\title{How do we get from object recognition\\ to object naming?} % Replace with your title

\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}

\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV18SubNumber}

\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper. LNCS guidelines
indicate it should be at least 70 and at most 150 words. It should be set in 9-point
font size and should be inset 1.0~cm from the right and left margins.
\dots
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

\section{Introduction}

Real-world objects are members of many categories. 
and speakers can typically between choose between different, more or less specific names when referring to a particular visual entity. 
For instance, the entity surrounded by the green box in Figure \ref{fig:example} is an instance of the categories \textit{female child, child, female, person, organism}, etc.\  and can be referred to with names such as e.g.\ \textit{girl, kid, cutie, daughter, person, human}.
But even though almost every task in language \& vision involves the prediction of object names (e.g. image captioning, referring expression generation, visual dialogue), hardly any research has explicitly looked at object naming, i.e.\ determining the actual word/linguistic concept that speakers would use to refer to an object (in a particular context), but see \cite{Ordonez:2016,zarriess-schlangen:2017}.
Even research in pragmatics, that traditionally deals with reference and referring expression production, has mostly focussed on attributes, rather than object names.
Recently, however, \cite{graf2016animal} have shown that object naming preferences are subject to contextual constraints and pragmatic factors: in a typical reference game set-up with images of target objects surrounded by distractor objects, speakers have been found to flexibly adjust object names depending on the context. For instance, a \textit{dalmatian} would be called \textit{dalmatian} in the context of other dogs or simply \textit{dog} when none of the distractors is also a dog.
This extends previous traditional work on concepts suggesting that the typicality of a referent determines its entry-level category (and consequently, its name) \cite{Rosch1978}.

On the vision side, however, there is huge body of research on object recognition, i.e.\ labeling visual objects according to a set of categories, cf.\ \cite{simonyan2014very,deng2014large,googlenet}.

\begin{figure}
\centering
\includegraphics[height=3.5cm]{fig/flickr_1000268201_boxes}
\caption{INCLUDE MSCOCO examples}
\label{fig:example}
\end{figure}

\section{Background}

\section{Data}

\subsection{Corpora}

\paragraph{Referring Expressions}
We analyze the RefCOCO and RefCOCO+ datasets which contain referring expressions to objects in MSCOCO \cite{mscoco} images.
These data collections were performed via crowdsourcing with the ReferIt Game \cite{Kazemzadeh2014}  where two players were paired and a director needed to refer to a predetermined object to a matcher, who then selected it.
RefCOCO and RefCOCO+ contain 3 referring expressions on average per object, and overall 150K expressions for 50K objects. 
The two datasets have been collected for an (almost) identical set of objects, but in RefCOCO+, players were asked not to use location words (\textit{on the left}, etc.).
See \cite{Yu2016} for more details.

\paragraph{Image Captions}

TODO.

\subsection{Preprocessing}

We parse referring expressions and captions with the Stanford Dependency Parser.
We extract heads/object names as follows: TODO.

\section{Names: Levels of specificity}

In this Section, we investigate whether variability of reference level can be observed in existing data sets for language \& vision.

\subsection{Using WordNet}

\cite{graf2016animal} investigate object naming with respect to reference level. They distinguish and manually annotate 3 levels: (i) sub-level (\textit{dalmatian}), (ii) basic-level (\textit{dog}), (iii) super-level (\textit{animal}).

For large-scale studies of object naming, we need to be able to automatically define the level of specificity of a name, given an ontology. 
In this Section, we investigate whether WordNet is appropriate for defining reference level. We hypothesize that the distance of a name's synset to the root node (entity) relates to its specificity.

\paragraph{Specifcity} We calculate this distance as follows: we lookup all synsets of a word and retrieve the respective paths to the root node in WordNet. 
For each word, we use the minimal path length as distance to the root node.

Table \ref{tab:specnames} shows the levels of specificity we observe for object names in the RefCoco data set.
We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels as the three-way classification adopted by \cite{graf2016animal}.

Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, here are some problematic examples from Table \ref{tab:specnames}:

\begin{itemize}
\item elephant (10) is more specific than panda (14)? horse is less specific than elephant (10)?
\end{itemize}

\begin{table}
\centering
\setlength{\tabcolsep}{4pt}
\begin{tabular}{rrl}
\toprule
 specificity &  rel.freq. &                          top 5 names \\
\midrule
          -1 &   0.071697 &      NONE,brocolli,zeb,broc,girafe \\
           2 &   0.003898 &                         thing,things \\
           3 &   0.001182 &   object,group,set,substance,objects \\
           4 &   0.140633 &           man,person,piece,head,part \\
           5 &   0.100739 &       player,glass,baby,front,corner \\
           6 &   0.208590 &              woman,girl,kid,boy,bowl \\
           7 &   0.238708 &            guy,right,chair,lady,bear \\
           8 &   0.110613 &           horse,bus,cow,pizza,batter \\
           9 &   0.097390 &         shirt,car,bike,donut,catcher \\
          10 &   0.048368 &   elephant,couch,truck,vase,suitcase \\
          11 &   0.008828 &    motorcycle,clock,mom,dad,scissors \\
          12 &   0.002822 &  oven,airplane,suv,taxi,refrigerator \\
          13 &   0.005253 &   laptop,fridge,canoe,orioles,pigeon \\
          14 &   0.000414 &  panda,freezer,penguin,rooster,rhino \\
          15 &   0.030870 &   zebra,giraffe,zebras,giraffes,deer \\
          16 &   0.000083 &       bison,mooses,orang,elks,sambar \\
          17 &   0.000143 &           ox,cattle,gnu,mustang,orca \\
\bottomrule
\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level, relative frequency and 5 most frequent names are shown}
\label{tab:specnames}
\end{table}

\clearpage

\bibliographystyle{splncs}
\bibliography{naming}
\end{document}

>>>>

\cite{graf2016animal}
\cite{Rosch1978}
\subsection{Intro to Problem}

\subsection{Definition Sub-, basic-, super-level Categories}
\cite{graf2016animal} investigate object naming with respect to reference level. They distinguish and manually annotate 3 levels: (i) sub-level (\textit{dalmatian}), (ii) basic-level (\textit{dog}), (iii) super-level (\textit{animal}).

\section{Requirements: What Do We Need? \cs{[Subsection of \ref{sec:object_naming}?]}}
For large-scale studies of object naming, we need to be able to automatically define the level of specificity of a name, given an ontology.
